---
title: "P8105_HW3_zc2555"
author: "Ziyu Chen"
date: "10/18/2021"
output: github_document
---

_r setup & loading packages_
```{r}
library(p8105.datasets)
data("instacart")
library(tidyverse)
library(ggplot2)
library(dplyr)
```

#Problem 1

_Q1: How many aisles are there, and which aisles are the most items ordered from?_

```{r}
aisles_count =
  instacart %>%
  count(aisle, sort=TRUE)

aisles_count
```

There are 134 aisles in the instacart dataset, fresh vegatables have the most times, which is 150609. 


_Q2: Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it_

```{r}
aisle_count = instacart %>%
  count(aisle,sort=TRUE) %>%
  filter(n>10000)

ggplot(aisle_count,aes(x=reorder(aisle, -n),y=n))+
  geom_bar(stat='identity')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Count of aisles")+
  xlab("Aisles")+
  ylab("Order Count")
```

The top three aisles are fresh vegetables, fresh furit and packaged vegetables fruit.


_Q3: Make a table showing the three most popular items_


```{r}
instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle, product_name) %>%
  summarise(
    product_count = n()) %>%
  mutate(
    product_rank = min_rank(-product_count)) %>%
  filter(product_rank <=3) %>%
  select(-product_rank) %>%
  knitr::kable()
```


_Q4: make a Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table_


```{r}
mean_hour=
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
   group_by (product_name, order_dow) %>%
   summarise(mean_hour = mean(order_hour_of_day)) %>%
   pivot_wider(names_from =order_dow, values_from =mean_hour) 

colnames(mean_hour)=c('', 'Sun', 'Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat')

mean_hour %>%
   knitr::kable()
```


#Problem 2

_load the data_
```{r}
library(p8105.datasets)
data("brfss_smart2010")
```








