---
title: "P8105_HW3_zc2555"
author: "Ziyu Chen"
date: "10/18/2021"
output: github_document
---

_r setup & loading packages_
```{r}
library(p8105.datasets)
data("instacart")
library(tidyverse)
library(ggplot2)
library(dplyr)
```

#Problem 1

_Q1: How many aisles are there, and which aisles are the most items ordered from?_

```{r}
aisles_count =
  instacart %>%
  count(aisle, sort=TRUE)

aisles_count
```

There are 134 aisles in the instacart dataset, fresh vegatables have the most times, which is 150609. 


_Q2: Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it_

```{r}
aisle_count = instacart %>%
  count(aisle,sort=TRUE) %>%
  filter(n>10000)

ggplot(aisle_count,aes(x=reorder(aisle, -n),y=n))+
  geom_bar(stat='identity')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Count of aisles")+
  xlab("Aisles")+
  ylab("Order Count")
```

